\cvsection{Volunteer Experience}
\begin{cventries}
  \cventry
    {Computer Science Department Representative}
    {Science Students' Society}
    {University of Calgary}
    {April 2015 - Present}
    {
      \begin{cvitems}
        \item {Create a Facebook group to share opportunities, events, and resources for undergraduate students.}
        \item {Coordinate and lead workshops such as the Google Design Sprint for Mobile and web languages.}
      \end{cvitems}
    }
  \cventry
    {Digital Projects Team Lead}
    {Women in Science and Engineering}
    {University of Calgary}
    {April 2015 - Present}
    {
      \begin{cvitems}
        \item {Improving the online presence for the club by designing a Wordpress website.}
        \item {Creating wireframes, comprehensive design layouts, and content to explain the club, executive team, and a news system.}
      \end{cvitems}
    }
  \cventry
    {Lead Instructor}
    {Girls Learning Code}
    {Calgary, Canada}
    {May 2013 - Present}
    {
      \begin{cvitems}
        \item {Assist workshop attendees with their technical educational pursuits.}
        \item {Created slide decks and taught programming concepts, Scratch, HTML, CSS, branding, and design.}
      \end{cvitems}
    }
  \cventry
    {President}
    {Computer Science Undergraduate Society}
    {Calgary, Canada}
    {May 2014 - April 2015}
    {
      \begin{cvitems}
        \item {Organized a group of executives to plan social, academic and career-focused events for the undergraduate population.}
        \item {Strengthened relations with industry representatives and staff members to present at events for the undergraduates.}
        \item {Co-created a Resource section for students by including class notes, websites, and online videos to supplement their education.}
      \end{cvitems}
    }
  \cventry
    {Demonstration Organizer and Participant}
    {NSERC Surfnet Workshop}
    {University of Calgary}
    {June 2013}
    {
      \begin{cvitems}
        \item {Helped organize demonstrations in the Taylor Family Digital Library and Interactions Lab for the 2013 Surfnet workshop.}
        \item {Presented research on representing products visually as a fingerprint, which highlights their differences.}
      \end{cvitems}
    }
  \cventry
    {Member and Competitor}
    {Problem Solving Club}
    {University of Calgary}
    {October 2012 - Present}
    {
      \begin{cvitems}
        \item {Attended meetings and practice contests to strengthen programming and problem solving skills.}
        \item {Achieved good standings in provincial programming competitions in a team of two or three.}
      \end{cvitems}
    }
\end{cventries}
