\cvsection{Relevant Experience}
\begin{cventries}
  \cventry
    {Student Assistant}
    {Operating Systems Group}
    {TU Dresden}
    {July 2014 - December 2014}
    {
      \begin{cvitems}
      \item {ELKVM is a virtual machine replication framework for x86/amd64 using KVM
      ontop of Linux. I ported the framework to the ARMv7 big.LITTLE
      architecture using KVM/ARM.}
      \end{cvitems}
    }
  \cventry
    {Google Summer of Code Student}
    {RTEMS}
    {}
    {March 2013 - September 2013}
    {
      \begin{cvitems}
      \item {POK (Partitioned OS Kernel) is an ARINC653 compliant OS. In my
	  project, it hosted and separated several RTEMS instances, to achieve
      ARINC653 compliance for RTEMS, too. It proved to be complicated to extend
      POK's functionality to forward interrupts to the user-space RTEMS
      instance. I presented a paper about this project on the 15th Real-Time Linux
    Workshop 2013, Switzerland.}
      \end{cvitems}
    }
  \cventry
    {RTEMS Training}
    {RTEMS \& Embedded Brains}
    {Munich, Germany}
    {June 2013}
    {
      \begin{cvitems}
      \item {Attended a RTEMS training class in Munich and got a
	Certificatate.}
      \end{cvitems}
    }
  \cventry
    {Student Assistant}
    {Operating Systems Group}
    {TU Dresden}
    {April 2011 - September 2011}
    {
      \begin{cvitems}
      \item {Paravirtualization of RTEMS (Real-Time Executive for
	Multiprocessor Systems) on L4Re (L4 Runtime environment).}
      \end{cvitems}
    }
  \cventry
    {Employee}
    {Faculty Computing Center}
    {TU Dresden}
    {April 2010 - February 2011}
    {}
\end{cventries}
